Get CRediT

### 2023-01-16 RR_manuscript/supplementary_materials.Rmd

# Read in primary coding sheet
the_sheet <- "data/analyses/analyses_coding.csv"

# Read in google sheet and join it with review data and phd/prior belief
# data
msa_models_unique <- left_join(
  read_csv(the_sheet) %>% 
    filter(added_on_osf == "yes") %>% 
    select(
      animal, model_n, outcome, typicality_operationalization, 
      framework, model, temporal_window, random_effects, n_random, 
      n_predictors, operationalisation, n_terms, n_coefficients, n_random_int, 
      n_random_slo, n_random_smooth, n_models
      ) %>%
    distinct(), 
  readRDS("./data/peer_review/msa_reviews.rds") %>% 
    select(animal = Q3, phon_rating = Q5_2, stat_rating = Q5_3, 
           all_rating = Q5_4) %>% 
    group_by(animal) %>% 
    # Remove ratings from 2 teams that dropped
    filter(!(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
    summarize(phon_rating = median(phon_rating), 
              stat_rating = median(stat_rating), 
              all_rating = median(all_rating)), 
  by = "animal"
) %>% 
  left_join(., 
    read_csv("./data/questionnaires/msa_intake_form_untidy.csv") %>%
      filter(added_on_osf == "yes", 
        !(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
      select(animal, years_from_phd, prior_belief), 
    by = "animal"
  )

>>>>

# Read in primary coding sheet
the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"

# Read in google sheet and join it with review data and phd/prior belief
# data
msa_models_unique <- left_join(
  read_sheet(the_sheet) %>% 
    filter(added_on_osf == "yes") %>% 
    select(
      animal, model_n, outcome, typicality_operationalization, 
      framework, model, temporal_window, random_effects, n_random, 
      n_predictors, operationalisation, n_terms, n_coefficients, n_random_int, 
      n_random_slo, n_random_smooth, n_models
      ) %>%
    distinct(), 
  readRDS("./data/peer_review/msa_reviews.rds") %>% 
    select(animal = Q3, phon_rating = Q5_2, stat_rating = Q5_3, 
           all_rating = Q5_4) %>% 
    group_by(animal) %>% 
    # Remove ratings from 2 teams that dropped
    filter(!(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
    summarize(phon_rating = median(phon_rating), 
              stat_rating = median(stat_rating), 
              all_rating = median(all_rating)), 
  by = "animal"
) %>% 
  left_join(., 
    read_csv("./data/questionnaires/msa_intake_form_untidy.csv") %>%
      filter(added_on_osf == "yes", 
        !(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
      select(animal, years_from_phd, prior_belief), 
    by = "animal"
  )

### 2023-01-16 scripts/r/04-1_refitted.Rmd

```{r coding}
the_sheet <- "data/analyses/analyses_coding.csv"

coding <- read_csv(the_sheet) %>%
  drop_na(model_n)
```

@@

```{r intake}
other_sheet <- "data/metadata/team_animal_coord.csv"

team_animal_coord <- read_csv(other_sheet)

>>>>

```{r coding}
the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"

coding <- read_sheet(the_sheet) %>%
  drop_na(model_n)
```

@@

```{r intake}
other_sheet <- "https://docs.google.com/spreadsheets/d/1KAZC2vyteTfGE6mlwOiz9b8F9VghDYLGsOzmWaNbmEE/edit?usp=sharing"

team_animal_coord <- read_sheet(other_sheet)

### 2023-01-16 scripts/r/09_credit_taxonomy.Rmd

n_countries <- contributors %>% 
  count(primary_affiliation_country, flag) %>% 
  arrange(n) %>% 
  mutate(
    country = primary_affiliation_country, 
    labs = case_when(
      country == "Australia" ~ glue("{open}'https://img.icons8.com/emoji/512/australia-emoji.png'{close}"), 
      country == "Hong Kong SAR, China" ~ glue("{open}'https://emojipedia-us.s3.dualstack.us-west-1.amazonaws.com/thumbs/120/apple/325/flag-hong-kong-sar-china_1f1ed-1f1f0.png'{close}"), 
      country == "Nigeria" ~ glue("{open}'https://img.icons8.com/emoji/512/nigeria-emoji.png'{close}"), 
      country == "Norway" ~ glue("{open}'https://img.icons8.com/emoji/512/norway-emoji.png'{close}"), 
      country == "Saudi Arabia" ~ glue("{open}'https://img.icons8.com/emoji/512/saudi-arabia-emoji.png'{close}"), 
      country == "Serbia" ~ glue("{open}'https://img.icons8.com/emoji/512/serbia-emoji.png'{close}"), 
      country == "Switzerland" ~ glue("{open}'https://img.icons8.com/emoji/512/switzerland-emoji.png'{close}"),
      country == "Austria" ~ glue("{open}'https://img.icons8.com/emoji/512/austria-emoji.png'{close}"),
      country == "Russia" ~ glue("{open}'https://img.icons8.com/emoji/512/russia-emoji.png'{close}"),
      country == "Spain" ~ glue("{open}'https://img.icons8.com/emoji/512/spain-emoji.png'{close}"),
      country == "Brazil" ~ glue("{open}'https://img.icons8.com/emoji/512/brazil-emoji.png'{close}"),
      country == "Netherlands" ~ glue("{open}'https://img.icons8.com/emoji/512/netherlands-emoji.png'{close}"),
      country == "New Zealand" ~ glue("{open}'https://img.icons8.com/emoji/512/new-zealand-emoji.png'{close}"),
      country == "Canada" ~ glue("{open}'https://img.icons8.com/emoji/512/canada-emoji.png'{close}"),
      country == "France" ~ glue("{open}'https://img.icons8.com/emoji/512/france-emoji.png'{close}"),
      country == "Germany" ~ glue("{open}'https://img.icons8.com/emoji/512/germany-emoji.png'{close}"),
      country == "United Kingdom" ~ glue("{open}'https://img.icons8.com/emoji/512/united-kingdom-emoji.png'{close}"),
      country == "United States" ~ glue("{open}'https://img.icons8.com/emoji/512/united-states-emoji.png'{close}")
    ), 
    primary_affiliation_country = fct_reorder(primary_affiliation_country, n, max))

n_countries %>% 
  ggplot() + 
  aes(x = n, y = primary_affiliation_country) + 
  geom_segment(aes(x = 0, xend = n, yend = primary_affiliation_country)) + 
  geom_point() + 
  labs(x = "n", y = NULL, title = "Number of analysts by country") + 
  theme_bw(base_size = 9) + 
  scale_y_discrete(name = NULL, labels = n_countries$labs) + 
  theme(axis.text.y = element_markdown(color = "black"))

>>>>

n_countries <- contributors %>% 
  count(primary_affiliation_country, flag) %>% 
  arrange(n) %>% 
  mutate(
    country = primary_affiliation_country, 
    labs = case_when(
      country == "Australia" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/australia-emoji.png'{close}"), 
      country == "Hong Kong SAR, China" ~ 
        glue("{open}'https://emojipedia-us.s3.dualstack.us-west-1.amazonaws.com/thumbs/120/apple/325/flag-hong-kong-sar-china_1f1ed-1f1f0.png'{close}"), 
      country == "Nigeria" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/nigeria-emoji.png'{close}"), 
      country == "Norway" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/norway-emoji.png'{close}"), 
      country == "Saudi Arabia" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/saudi-arabia-emoji.png'{close}"), 
      country == "Serbia" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/serbia-emoji.png'{close}"), 
      country == "Switzerland" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/switzerland-emoji.png'{close}"),
      country == "Austria" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/austria-emoji.png'{close}"),
      country == "Russia" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/russia-emoji.png'{close}"),
      country == "Spain" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/spain-emoji.png'{close}"),
      country == "Brazil" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/brazil-emoji.png'{close}"),
      country == "Netherlands" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/netherlands-emoji.png'{close}"),
      country == "New Zealand" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/new-zealand-emoji.png'{close}"),
      country == "Canada" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/canada-emoji.png'{close}"),
      country == "France" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/france-emoji.png'{close}"),
      country == "Germany" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/germany-emoji.png'{close}"),
      country == "United Kingdom" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/united-kingdom-emoji.png'{close}"),
      country == "United States" ~ 
        glue("{open}'https://img.icons8.com/emoji/512/united-states-emoji.png'{close}")
    ), 
    country = fct_reorder(country, n, max))

n_countries %>% 
  ggplot() + 
  aes(x = n, y = country) + 
  geom_segment(aes(x = 0, xend = n, yend = country), size = 2, 
    color = "grey25", lineend = "round") + 
  geom_point(size = 6) + 
  geom_text(aes(label = n), color = "white", size = 3) + 
  labs(x = "n", y = NULL, 
    title = "Number of analysts by country", 
    subtitle = glue("(n = {sum(n_countries$n)})")) + 
  theme_bw(base_size = 13, base_family = "Times") + 
  scale_y_discrete(name = NULL, labels = n_countries$labs) + 
  theme(axis.text.y = element_markdown(color = "black", vjust = 0.65), 
    panel.grid.major = element_line(colour = 'grey90', size = 0.15),
    panel.grid.minor = element_line(colour = 'grey90', size = 0.15))

n_countries %>% 
  arrange(desc(n)) %>% 
  transmute(Country = glue("{flag} {country}"), n) %>% 
  knitr::kable(format = "pandoc")
```
